Output Summary

### 2023-08-18 03-post-process/output-plots-children/12-pp-checks.Rmd
Rename resid and pp-check diag Rmd sections

## Posterior Predictive Checks

This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model.
For each observed data point and MCMC iteration, a value was simulated from the model.
The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated.

@@

  * **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation. This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities by performing calculations on the square root of observed and expected counts..
This applies to all composition data, the survival from BON to LGR data, and the spawn status data.

>>>>

# Posterior Predictive Checks

This output is a diagnostic of the consistency of variability in the data with the variability assumed by the model, similar to the residual diagnostic section.
For each observed data point and MCMC iteration, a value was simulated from the model.
The fit of the observed and simulated data was calculated, and the proportion of MCMC iterations in which the observed data fitted more poorly than the simulated data (i.e., a Bayesian p-value) was calculated.

@@

* **Log-normal**: squared difference of the log-scale observation and log-scale expectation. This applies to all abundance data.
* **Logit-normal**: squared difference of the logit-scale observation and logit-scale expectation. This applies to all survival data, except the BON to LGR and the pre-spawn survival which were fitted using binomial distributions.
* **Binomial/Multinomial**: Freeman-Tukey fit statistic, which is similar to the $\chi^2$ statistic but better handles small bin probabilities by performing calculations on the square root of observed and expected counts.
This applies to all composition data and the survival from BON to LGR data.

### 2023-08-18 03-post-process/output-plots.Rmd
Rename resid and pp-check diag Rmd sections

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
    value: TRUE
  include_parr_recruitment:
    label: "Include Parr Recruitment Output?"
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_processes:
    label: "Include Misc. Processes Output?"
    value: TRUE
  include_composite_rates:
    label: "Include Composite Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: TRUE
  include_noise_term_diags:
    label: "Include Noise Term Diagnostic Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_known:
     label: "Include Non-Stochastic Quantities?"
     value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

@@

```{r noise-term-diags, child = "output-plots-children/11-noise-term-diags.Rmd", eval = params$include_noise_term_diags}
```

>>>>

---
title: "Output Summary"
subtitle: "`r paste0('Model Scenario: ', params$scenario)`" 
date: "`r paste0('Date Rendered: ', Sys.Date())`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base_vlong"
    input: text
  thin_percent:
    label: "Proportion of Posterior Samples to Retain?"
    value: 1
    input: numeric
  include_sim_years:
    label: "Include Simulated Years on Plots?"
    value: FALSE
  include_mcmc_diags:
    label: "Include MCMC Diagnostic Output?"
    value: TRUE
  include_fit_to_data:
    label: "Include Model Fit Output?"
    value: TRUE
    value: TRUE
  include_parr_recruitment:
    label: "Include Parr Recruitment Output?"
  include_mean_length:
    label: "Include Mean Length Output?"
    value: TRUE
  include_surv_vs_length:
    label: "Length-based Survival Output?"
    value: TRUE
  include_capacity_vs_habitat:
    label: "Include Capacity vs. Habitat Output?"
    value: TRUE
  include_misc_processes:
    label: "Include Misc. Processes Output?"
    value: TRUE
  include_composite_rates:
    label: "Include Composite Rate Output?"
    value: TRUE
  include_rho_params:
    label: "Include Process Model Correlation Output?"
    value: FALSE
  include_residual_diags:
    label: "Include Residual Diagnostic Output?"
    value: FALSE
  include_pp_check:
    label: "Include Posterior Predictive Check Output?"
    value: TRUE
  include_param_summaries:
    label: "Include Posterior Boxplot Output?"
    value: TRUE
  include_post_v_prior:
    label: "Include Posterior vs. Prior Densities?"
    value: TRUE
  include_known:
     label: "Include Non-Stochastic Quantities?"
     value: TRUE
  include_jags_info:
    label: "Include JAGS Code/Data?"
    value: TRUE
editor_options: 
  chunk_output_type: console
---

@@

```{r noise-term-diags, child = "output-plots-children/11-resid-diags.Rmd", eval = params$include_resid_diags}
```

```{r pp-check, child = "output-plots-children/12-pp-checks.Rmd", eval = params$include_pp_check & model_info$do_pp_check}
```
